---
title: "Are Michelin-starred Restaurants Predictable?"
author: "Grant Cho"
date: "4/25/2020"
output: html_document
---

# Setting up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(randomForest, tree, ISLR, rpart, rattle, pROC, partykit, ggplot2, glmnet, leaps, dplyr, data.table, tm, RColorBrewer, wordcloud, ranger, JOUSBoost, gbm, neuralnet, keras, tensorflow, SnowballC, magrittr, httr, rvest, stringr, topicmodels, readr, tidyr, syuzhet, tidytext, corrplot, modelr)

michelin.data <- read.csv("nycmichelin.csv")
nyc.data <- read.csv("newyorkrestaurants.csv")
michelin.trip <- read.csv("merge.csv")
```

# Cleaning the Michelin Data

```{r}
michelin.trip <- michelin.trip[,-(1:2)] #removing superfluous columns from the webscraping

michelin.trip <- michelin.trip[,c(17, 1:16)]

michelin.trip$Cuisine <- NULL

michelin.trip$Five.stars <- as.numeric(michelin.trip$Five.stars)
michelin.trip$Four.stars <- as.numeric(michelin.trip$Four.stars)
michelin.trip$Three.stars <- as.numeric(michelin.trip$Three.stars)
michelin.trip$Two.stars <- as.numeric(michelin.trip$Two.stars)
michelin.trip$One.star <- as.numeric(michelin.trip$One.star)

michelin.trip <- michelin.trip %>% mutate(Overall.Rating = (Five.stars*5 + Four.stars*4 + Three.stars*3 + Two.stars*2 + One.star)/(Five.stars + Four.stars + Three.stars + Two.stars + One.star))

michelin.trip <- michelin.trip[,-2]

sum.trip.data <- michelin.trip %>% group_by(Restaurant, Food.rating, Service.rating, Value.rating, Atmosphere.rating, Price.range, Awards, Number.of.reviews, Overall.Rating) %>% summarise(Review.feedback = paste(Review.text, collapse = ""), Review.title = paste(Review.titles, collapse = ""))

sum.trip.data
```

```{r}
#Michelin Data Wrangling
michelin.data <- michelin.data[,-(1:4)] #removing superfluous columns from the webscraping

michelin.data <- michelin.data %>% mutate(michelin.star = ifelse(Michelin.stars == "m", 1, ifelse(Michelin.stars == "n", 2, 3))) #m = 1 star, n = 2 stars, o = 3 stars

michelin.data <- michelin.data[,-(ncol(michelin.data)-1)] #getting rid of the original webscraped Michelin data

michelin.data <- cbind(michelin.data, as.data.frame(word(michelin.data$Cuisine.and.Price, -1))) #creating and merging the Cuisine dataframe with the original dataframe 

colnames(michelin.data)[ncol(michelin.data)] <- "Cuisine"

michelin.data <- michelin.data %>% separate(Cuisine.and.Price, into = c("Average.Min.Price", sep = " "))

michelin.data <- michelin.data[,-3]

michelin.data$Average.Min.Price <- as.numeric(michelin.data$Average.Min.Price)

michelin.data <- michelin.data %>% mutate(Dining.Type = ifelse(Average.Min.Price >= 50, "Fine", "Casual"))

colnames(michelin.data)[ncol(michelin.data)-2] <- "Michelin.Stars"

michelin.data
```

# Cleaning the NYC TripAdvisor data

```{r}
nyc.data <- nyc.data[,c(23,1:22)]

nyc.data <- nyc.data[,-c(2,3,14)]

nyc.data <- nyc.data[,-2]

nyc.data$Five.stars <- as.numeric(nyc.data$Five.stars)
nyc.data$Four.stars <- as.numeric(nyc.data$Four.stars)
nyc.data$Three.stars <- as.numeric(nyc.data$Three.stars)
nyc.data$Two.stars <- as.numeric(nyc.data$Two.stars)
nyc.data$One.star <- as.numeric(nyc.data$One.star)

nyc.data <- nyc.data %>% mutate(Overall.Rating = (Five.stars*5 + Four.stars*4 + Three.stars*3 + Two.stars*2 + One.star)/(Five.stars + Four.stars + Three.stars + Two.stars + One.star)) #Calculating overall rating by weighting the review stars
```

```{r}
sum.data <- nyc.data %>% group_by(Restaurant, Cuisine, Food.rating, Service.rating, Value.rating, Atmosphere.rating, Price.range, Awards, Number.of.reviews, Overall.Rating) %>% summarise(Review.feedback = paste(Review.text, collapse = ""), Review.title = paste(Review.titles, collapse = ""))

filtered.data <- sum.data %>% filter(Food.rating != "null")
```

```{r}
filtered.data1 <- left_join(filtered.data, michelin.data, "Restaurant")

filtered.data1 <- filtered.data1[,c(1:12, 15)]

filtered.data1$Michelin.Stars <- ifelse(is.na(filtered.data1$Michelin.Stars == TRUE), 0, filtered.data1$Michelin.Stars)

colnames(filtered.data1)[2] <- "Cuisine.x"

filtered.data1$Dining.Type <- ifelse(substr(filtered.data1$Price.range, 1, 3) == "$$$", "Fine", "Casual")

michelin.filter <- filtered.data1 %>% filter(Michelin.Stars > 0)
```

```{r}
michelin.not.included <- merge(michelin.data, sum.trip.data, by = "Restaurant")
michelin.not.included <- michelin.not.included[,-c(2:3)]
michelin.not.included <- michelin.not.included[,c(1,3,5:14,2,4)]
michelin.not.included$Restaurant <- as.character(michelin.not.included$Restaurant)
michelin.not.included <- michelin.not.included[,c(1:2,14,13,8,10,3:7,9,11:12)]
colnames(michelin.not.included)[2] <- "Cuisine.x"
michelin.not.included

michelin.final <- dplyr::bind_rows(michelin.filter, michelin.not.included) #rbind isn't working properly HERE

michelin.final <- michelin.final[,c(1:4,6:11,5,12:14)]
michelin.final$Dining.Type <- as.factor(michelin.final$Dining.Type)
```

```{r}
filtered.data1 <- filtered.data1[,c(1,14,13,2,9,8,10,3:7,11:12)]

filtered.data2 <- filtered.data1 %>% filter(Michelin.Stars == 0)

nyc.cleaned.data <- dplyr::bind_rows(filtered.data2, michelin.final)

nyc.cleaned.data <- nyc.cleaned.data[,-12]

nyc.cleaned.data <- nyc.cleaned.data %>% separate(Number.of.reviews, into = c("Review.count", sep = " "))

nyc.cleaned.data$Review.count <- as.numeric(nyc.cleaned.data$Review.count)

nyc.cleaned.data <- nyc.cleaned.data[,-6]
```

# Final Cleaned Data

```{r}
nyc.cleaned.data$Food.rating <- as.numeric(as.character(nyc.cleaned.data$Food.rating))/10

nyc.cleaned.data$Service.rating <- as.numeric(as.character(nyc.cleaned.data$Service.rating))/10

nyc.cleaned.data$Value.rating <- as.numeric(as.character(nyc.cleaned.data$Value.rating))/10

nyc.cleaned.data$Atmosphere.rating <- as.numeric(as.character(nyc.cleaned.data$Atmosphere.rating))/10

nyc.cleaned.data
```

```{r}
#Determining the number of years a restaurant holds an award

model.df <- nyc.cleaned.data

model.df1 <- model.df %>% mutate(Award.years = as.character(regmatches(model.df$Awards,gregexpr("[[:digit:]]+\\.*[[:digit:]]*",model.df$Awards))))

award.years <- as.data.frame(gsub("[^0-9]+", "", model.df1$Award.years))

colnames(award.years)[1] <- "award.year"

award.years$award.year <- as.character(award.years$award.year)

award.years <- award.years %>% mutate(number.of.years = ifelse(nchar(award.year) == 4, 1, ifelse(nchar(award.year) == 8, 2, ifelse(nchar(award.year) == 12, 3, 0))))

model.df2 <- cbind(model.df, award.years)

model.df2 <- model.df2[,-c(6,14)]

colnames(model.df2)[13] <- "years.with.tripadvisor.award"

model.df3 <- model.df2[,c(1,4,2:3,13,7:10,6,5,12,11)]

colnames(model.df3)[2] <- "Cuisine"

final.model.df <- model.df3

final.model.df
```

```{r}
#Creating the Sentiment Analysis column
sentiment <- c()

for(i in 1:1571){
corp.sent <- VCorpus(VectorSource(as.character(model.df$Review.feedback[i])))
corps = tm_map(corp.sent, removePunctuation) 
corps = tm_map(corps, removeNumbers) 
corps = tm_map(corps, content_transformer(tolower), lazy=TRUE) 
corps = tm_map(corps, content_transformer(removeWords), c("TIL") ,lazy=TRUE) 
corps = tm_map(corps, stripWhitespace)
corps = tm_map(corps, content_transformer(removeWords), stopwords("SMART"), lazy=TRUE)

dtms <- TermDocumentMatrix(corps)
dtms.matrix <- as.matrix(dtms)
dtms.sum <- sort(rowSums(dtms.matrix), decreasing = TRUE)
dtms.df <- data.frame(word = names(dtms.sum), freq = dtms.sum)
sentiment <- c(sentiment, mean(get_sentiment(as.character(dtms.df$word))))
}
```

```{r}
cleaned.data <- cbind(final.model.df, as.data.frame(sentiment))

no.na <- cleaned.data %>% na.omit()

mean(no.na$Atmosphere.rating)
mean(no.na$Service.rating)
mean(no.na$Value.rating)
mean(no.na$Food.rating)

cleaned.data <- cleaned.data %>% mutate(Atmosphere.rating =ifelse(is.na(Atmosphere.rating), mean(no.na$Atmosphere.rating), Atmosphere.rating))

cleaned.data <- cleaned.data %>% mutate(Service.rating = ifelse(is.na(Service.rating), mean(no.na$Service.rating), Service.rating))

cleaned.data <- cleaned.data %>% mutate(Value.rating = ifelse(is.na(Value.rating), mean(no.na$Value.rating), Value.rating))

cleaned.data <- cleaned.data %>% mutate(Food.rating = ifelse(is.na(Food.rating), mean(no.na$Food.rating), Food.rating))

cuisine.names <- names(abs(sort(-table(cleaned.data$Cuisine))))

cuisine.names <- cuisine.names[1:39]

cleaned.data$Cuisine <- as.character(cleaned.data$Cuisine)

cleaned.data <- cleaned.data %>% mutate(Cuisine = ifelse(Cuisine %in% cuisine.names, Cuisine, "Other"))

cleaned.data <- cleaned.data %>% mutate(Have.Star = ifelse(Michelin.Stars > 0, 1, 0))

cleaned.data$Cuisine <- as.factor(cleaned.data$Cuisine)

cleaned.data$Dining.Type <- as.factor(cleaned.data$Dining.Type)

cleaned.data
```

# Exploratory Data Analysis (EDA)

```{r}
#Correlation matrix
cor.df <- cleaned.data[,-c(1:3,12:13)]

corr_mat <- cor(cor.df)
corrplot(corr_mat, type = 'upper', order = "hclust", sig.level = 0.05, insig = "blank", tl.col = "black", tl.srt = 45, addCoef.col = "black")
```

```{r}
norm.df <- as.data.frame(abs(sort(-table(cleaned.data$Cuisine))))

new.norm <- norm.df[1:7,]

mich <- cleaned.data %>% filter(Michelin.Stars > 0)

mich.df <- as.data.frame(abs(sort(-table(mich$Cuisine))))

mich.df1 <- mich.df[1:7,]

ggplot(data = new.norm, aes(x = Var1, y = Freq)) + geom_bar(stat="identity") + geom_bar(stat="identity", fill = "#339999") + theme_minimal() + ggtitle("Most Popular Cuisines for Restaurants without Michelin Stars") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Cuisine") + ylab("Count")

ggplot(data = mich.df1, aes(x = Var1, y = Freq)) + geom_bar(stat="identity", fill = "#CC0000") + theme_minimal() + ggtitle("Most Popular Cuisines for Restaurants with Michelin Stars") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Cuisine") + ylab("Count")
```

```{r}
avg.mich <- mich %>% group_by(Dining.Type) %>% summarise(Count = n())

avg.nyc <- cleaned.data %>% group_by(Dining.Type) %>% summarise(Count = n())

ggplot(data = avg.nyc, aes(x = Dining.Type, y = Count, fill = Dining.Type)) + geom_bar(stat="identity", position = "stack", fill = "#339999") + theme_minimal() + ggtitle("Type of Dining for all NYC restaurants") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Type of Dining") + ylab("Count")

ggplot(data = avg.mich, aes(x = Dining.Type, y = Count, fill = Dining.Type)) + geom_bar(stat="identity", position = "stack", fill = "#CC0000") + theme_minimal() + ggtitle("Type of Dining for Michelin-starred Restaurants") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Type of Dining") + ylab("Count")
```


```{r}
pie <- cleaned.data %>% dplyr::group_by(Michelin.Stars) %>% dplyr::summarise(n = dplyr::n())

ggplot(pie, aes(x = "", y = n, fill = factor(Michelin.Stars))) + geom_bar(width = 1, stat = "identity") + coord_polar("y", start = 0) + theme_minimal() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), plot.title = element_text(face = "bold")) + labs(fill = "Michelin Stars") + ggtitle("Michelin Star Rarity in NYC") + theme(plot.title = element_text(hjust = 0.5)) + scale_fill_brewer(palette = "Reds")
```

```{r}
ggplot(cleaned.data, aes(x = Michelin.Stars, y = Overall.Rating, group = Michelin.Stars, fill = factor(Michelin.Stars))) + geom_boxplot() + theme_minimal() + xlab("Michelin Stars") + ylab("Overall Rating") + ggtitle("Boxplot of Overall Rating against Michelin Stars") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_fill_brewer(palette = "Reds") + geom_jitter(shape = 1, position = position_jitter(0)) + labs(fill = "Michelin Stars")
```

```{r}
ggplot(cleaned.data, aes(x = Have.Star, y = Overall.Rating, group = Have.Star, fill = factor(Have.Star))) + geom_boxplot() + theme_minimal() + xlab("0 or ≥1 Michelin Star") + ylab("Overall Rating") + ggtitle("Boxplot of Overall Rating against Restaurants with at least one Michelin Star") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_fill_brewer(palette = "Reds") + geom_jitter(shape = 1, position = position_jitter(0)) + labs(fill = "≥ 1 Michelin Star")
```

# Text Analysis

```{r}
#3 Michelin Stars Text Analysis Set up
corp.nyc <- VCorpus(VectorSource(as.character(model.df$Review.feedback)))
corp4 = tm_map(corp.nyc, removePunctuation) 
corp4 = tm_map(corp4, removeNumbers) 
corp4 = tm_map(corp4, content_transformer(tolower), lazy=TRUE) 
corp4 = tm_map(corp4, content_transformer(removeWords), c("TIL") ,lazy=TRUE) 
corp4 = tm_map(corp4, stripWhitespace)
corp4 = tm_map(corp4, content_transformer(removeWords), stopwords("SMART"), lazy=TRUE)

dtm.4 <- TermDocumentMatrix(corp4)
dtm.4.matrix <- as.matrix(dtm.4)
dtm.4.sum <- sort(rowSums(dtm.4.matrix), decreasing = TRUE)
dtm.4.df <- data.frame(word = names(dtm.4.sum), freq = dtm.4.sum)
```

# Word Clouds

```{r, warning = FALSE}
#Word clouds for restaurants with 1 Michelin Star
set.seed(245)
wordcloud(words = dtm.4.df$word, freq = dtm.4.df$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r}
#Sentiment Analysis
mean(get_sentiment(as.character(dtm.4.df$word))) #Overall Michelin sentiment
```

Customers in New York City restaurants give generally neutral reviews overall.

# Michelin Reviews Text Analysis

```{r}
michelin.star <- model.df %>% filter(Michelin.Stars > 0)

one.michelin.star <- model.df %>% filter(Michelin.Stars == 1)

two.michelin.star <- model.df %>% filter(Michelin.Stars == 2)

three.michelin.star <- model.df %>% filter(Michelin.Stars == 3)
```

```{r}
#Overall Michelin Star Text Analysis
corp.star <- VCorpus(VectorSource(as.character(michelin.star$Review.feedback)))
corp5 = tm_map(corp.star, removePunctuation) 
corp5 = tm_map(corp5, removeNumbers) 
corp5 = tm_map(corp5, content_transformer(tolower), lazy=TRUE) 
corp5 = tm_map(corp5, content_transformer(removeWords), c("TIL") ,lazy=TRUE) 
corp5 = tm_map(corp5, stripWhitespace)
corp5 = tm_map(corp5, content_transformer(removeWords), stopwords("SMART"), lazy=TRUE)

dtm.5 <- TermDocumentMatrix(corp5)
dtm.matrix.5 <- as.matrix(dtm.5)
dtm.sum.5 <- sort(rowSums(dtm.matrix.5), decreasing = TRUE)
dtm.df.5 <- data.frame(word = names(dtm.sum.5), freq = dtm.sum.5)
```

```{r}
#One Michelin Star Text Analysis
corp.onestar <- VCorpus(VectorSource(as.character(one.michelin.star$Review.feedback)))
corp6 = tm_map(corp.onestar, removePunctuation) 
corp6 = tm_map(corp6, removeNumbers) 
corp6 = tm_map(corp6, content_transformer(tolower), lazy=TRUE) 
corp6 = tm_map(corp6, content_transformer(removeWords), c("TIL") ,lazy=TRUE) 
corp6 = tm_map(corp6, stripWhitespace)
corp6 = tm_map(corp6, content_transformer(removeWords), stopwords("SMART"), lazy=TRUE)

dtm.6 <- TermDocumentMatrix(corp6)
dtm.matrix.6 <- as.matrix(dtm.6)
dtm.sum.6 <- sort(rowSums(dtm.matrix.6), decreasing = TRUE)
dtm.df.6 <- data.frame(word = names(dtm.sum.6), freq = dtm.sum.6)
```

```{r}
#Two Michelin Stars Text Analysis
corp.twostar <- VCorpus(VectorSource(as.character(two.michelin.star$Review.feedback)))
corp7 = tm_map(corp.twostar, removePunctuation) 
corp7 = tm_map(corp7, removeNumbers) 
corp7 = tm_map(corp7, content_transformer(tolower), lazy=TRUE) 
corp7 = tm_map(corp7, content_transformer(removeWords), c("TIL") ,lazy=TRUE) 
corp7 = tm_map(corp7, stripWhitespace)
corp7 = tm_map(corp7, content_transformer(removeWords), stopwords("SMART"), lazy=TRUE)

dtm.7 <- TermDocumentMatrix(corp7)
dtm.matrix.7 <- as.matrix(dtm.7)
dtm.sum.7 <- sort(rowSums(dtm.matrix.7), decreasing = TRUE)
dtm.df.7 <- data.frame(word = names(dtm.sum.7), freq = dtm.sum.7)
```

```{r}
#Three Michelin Stars Text Analysis
corp.threestar <- VCorpus(VectorSource(as.character(three.michelin.star$Review.feedback)))
corp8 = tm_map(corp.threestar, removePunctuation) 
corp8 = tm_map(corp8, removeNumbers) 
corp8 = tm_map(corp8, content_transformer(tolower), lazy=TRUE) 
corp8 = tm_map(corp8, content_transformer(removeWords), c("TIL") ,lazy=TRUE) 
corp8 = tm_map(corp8, stripWhitespace)
corp8 = tm_map(corp8, content_transformer(removeWords), stopwords("SMART"), lazy=TRUE)

dtm.8 <- TermDocumentMatrix(corp8)
dtm.matrix.8 <- as.matrix(dtm.8)
dtm.sum.8 <- sort(rowSums(dtm.matrix.8), decreasing = TRUE)
dtm.df.8 <- data.frame(word = names(dtm.sum.8), freq = dtm.sum.8)
```

# Word Clouds

```{r, warning = FALSE}
#Word clouds for restaurants with at least 1 Michelin Star
set.seed(245)
wordcloud(words = dtm.df.5$word, freq = dtm.df.5$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r, warning = FALSE}
#Word clouds for restaurants with 1 Michelin Star
set.seed(245)
wordcloud(words = dtm.df.6$word, freq = dtm.df.6$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r, warning = FALSE}
#Word clouds for restaurants with 2 Michelin Stars
set.seed(245)
wordcloud(words = dtm.df.7$word, freq = dtm.df.7$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r, warning = FALSE}
#Word clouds for restaurants with 3 Michelin Stars
set.seed(245)
wordcloud(words = dtm.df.8$word, freq = dtm.df.8$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

# Sentiment Analysis

```{r}
#Sentiment Analysis
Sentiment <- c(mean(get_sentiment(as.character(dtm.4.df$word))),mean(get_sentiment(as.character(dtm.df.6$word))),mean(get_sentiment(as.character(dtm.df.7$word))),mean(get_sentiment(as.character(dtm.df.8$word))))

Stars <- c(0:3)

sentiment.df <- data.frame(Stars, Sentiment)

ggplot(data = sentiment.df, aes(x = Stars, y = Sentiment, fill = factor(Stars))) + geom_bar(stat = "identity") + theme_minimal() + ggtitle("Sentiment for restaurants with/without Michelin Stars") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Michelin Stars") + ylab("Feedback Sentiment") + scale_fill_brewer(palette = "Reds") + labs(fill = "Michelin Stars")
```

# Training and Testing data

```{r}
logit.data <- cleaned.data[,-c(1,4,12:13)] #removed restaurant names because of unique values
```

```{r}
set.seed(245)
n <- nrow(logit.data)
train.idx <- sample(n, round(0.75*n, 0))
data.train <- logit.data[train.idx, ] 
data.test <- logit.data[-train.idx, ]
```

# LASSO

```{r}
X <- model.matrix(Have.Star~., data.train)[,-1]
Y <- data.train$Have.Star
```

```{r}
set.seed(245) #set seed for replicability
fit.cv <- cv.glmnet(X, Y, alpha = 1, family = "binomial", nfolds = 10, type.measure = "auc")
plot(fit.cv) #finding the lambda value that yields the highest AUC
```

```{r}
coef.min <- coef(fit.cv, s = "lambda.min")
coef.min <- coef.min[which(coef.min != 0),]
as.matrix(coef.min)
beta.min <- rownames(as.matrix(coef.min))
beta.min #shows us the non-zero coefficients after LASSO has been applied
```

# Logistic Regression

```{r}
fit_logi <- glm(Have.Star~., data.train, family = binomial(logit))

#Backward selection
fit_logi2 <- glm(Have.Star~.-sentiment, data.train, family = binomial(logit))

fit_logi3 <- glm(Have.Star~.-sentiment-Service.rating, data.train, family = binomial(logit))

fit_logi4 <- glm(Have.Star~.-sentiment-Service.rating-Food.rating-Overall.Rating-Atmosphere.rating, data.train, family = binomial(logit))

summary(fit_logi4)

fit_logi5 <- glm(Have.Star~.-sentiment-Service.rating-Food.rating-Overall.Rating-Atmosphere.rating-years.with.tripadvisor.award, data.train, family = binomial(logit))

summary(fit_logi5)
```

Lowest AIC means the least amount of information is lost with this particular model.

```{r}
fit.logit.roc <- roc(response = data.train$Have.Star, predictor = fit_logi5$fitted, plot = T, col = "#CC0000", main = "Training data AUC curve")
plot(fit.logit.roc, col = "#CC0000")
legend("bottomright",
       c(paste0("fit.logit AUC=", round(fit.logit.roc$auc, 2))),
       col = c("#CC0000"),
       lty = 1)
fit.logit.roc$auc 
```

# Non-weighted Classification (Conservative model)

```{r}
fit.logit.pred0 <- ifelse(fit_logi5$fitted > 0.65, "1", "0") 
cm0 <- table(fit.logit.pred0, data.train$Have.Star)
cm0
(cm0[1,2]+cm0[2,1])/sum(cm0) #MCE
(cm0[2,2])/(cm0[2,2]+cm0[1,2]) #recall
(cm0[2,2])/(cm0[2,2]+cm0[2,1]) #precision
```

# Logistic Regression on Testing data (optimized for precision and conservative investors)

```{r}
fit.glm.pred.test0 <- predict(fit_logi5, data.test, type = "response") >= 0.65
cm.test0 <- table(fit.glm.pred.test0, data.test$Have.Star)
cm.test0[1,2]/sum(cm.test0) #MCE
cm.test0
```

Misclassification error of 0.025. Recall is 0 but so is the false positive rate.

# Weighted Classification (non-conservative/recall focused)

```{r}
fit.logit.pred <- ifelse(fit_logi5$fitted > 0.2, "1", "0") #0.17 = 0.2/(1+0.2) from Weighted classification error using Bayes' rule
cm <- table(fit.logit.pred, data.train$Have.Star)
cm
(cm[1,2]+cm[2,1])/sum(cm) #MCE
(cm[2,2])/(cm[2,2]+cm[1,2]) #recall
```

Recall

# Logistic Regression on Testing data

```{r}
fit.glm.pred.test <- predict(fit_logi5, data.test, type = "response") >= 0.2
cm.test <- table(fit.glm.pred.test, data.test$Have.Star)
cm.test
cm.test[1,2]/sum(cm.test) #MCE
(cm.test[2,2])/(cm.test[2,2]+cm.test[1,2]) #recall
```

```{r}
test.pred <- predict(fit_logi5, data.test, probability = TRUE)
fit.logit.roc.test <- roc(response = data.test$Have.Star, test.pred, plot = T, col = "#CC0000", main = "Testing data AUC curve")
plot(fit.logit.roc.test, col = "#CC0000")
legend("bottomright",
       c(paste0("fit.logit.test AUC=", round(fit.logit.roc.test$auc, 2))),
       col = c("#CC0000"),
       lty = 1)
fit.logit.roc.test$auc 
```

# Random Forest

```{r}
rf.data <- cleaned.data[,-c(1,4,12:13)] #removed restaurant names because of unique values
rf.data$Have.Star <- as.factor(rf.data$Have.Star)

set.seed(245)
n <- nrow(rf.data)
train.idx.rf <- sample(n, round(0.75*n, 0))
data.train.rf <- rf.data[train.idx.rf, ] 
data.test.rf <- rf.data[-train.idx.rf, ]
```

```{r}
fit.rf.train <- randomForest(Have.Star~., data.train.rf, mtry = 50, ntree = 500) 
plot(fit.rf.train, main = "") 
title("Random Forest")
legend("topright", colnames(fit.rf.train$err.rate), col = 1:3, cex=0.8, fill=1:3)
```

```{r}
predict.rf.y <- predict(fit.rf.train, newdata=data.test.rf, type = "response")
cm.rf <- table(predict.rf.y, data.test.rf$Have.Star)
round((cm.rf[1,2]+2*cm.rf[2,1])/sum(cm.rf), 3)

fit.rf.roc <- roc(data.test.rf$Have.Star, predict.rf.y)
plot(fit.rf.roc, col = "#339999")
legend("bottomright",
       c(paste0("fit.rf AUC=", round(fit.rf.roc$auc, 2))),
       col = c("#339999"),
       lty = 1)
fit.rf.roc$auc
```

```{r}
plot(1-fit.rf.roc$specificities,
     fit.rf.roc$sensitivities, col = "#339999", lwd = 2, type = "l",
     xlab = "False Positive",
     ylab = "Sensitivity")
lines(1-fit.logit.roc.test$specificities, fit.logit.roc.test$sensitivities, col = "#CC0000", lwd = 2)
legend("bottomright",
       c(paste0("fit.rf AUC=", round(fit.rf.roc$auc, 2)), 
         paste0("fit.logit.test AUC=", round(fit.logit.roc.test$auc, 2))),
       col = c("#339999", "#CC0000"),
       lty = 1)
```


```{r}
varImpPlot(fit.rf.train, main = "")
title("Variable Importance Plot")
```

Interestingly, `Cuisine` is considered the most powerful predictor in the model and `Food.rating` the least.

# Multiple Regression Analysis

```{r}
lm.data <- cleaned.data[,-c(1,12:13,15,17)]
```

```{r}
fit.lm <- lm(Michelin.Stars~., lm.data)

#Backward selection
fit.lm.final <- lm(Michelin.Stars~.-Food.rating-Value.rating-Atmosphere.rating-years.with.tripadvisor.award-Overall.Rating, lm.data)

summary(fit.lm.final)
```

# Generating the prediction data frame on recall-focused model

```{r}
fit.logit.pred0 <- ifelse(fit_logi5$fitted > 0.65, "1", "0") 
train.df0 <- predict(fit_logi5, data.train, type = "response") >= 0.65
train.final0 <- cbind(data.train, train.df0)
d0 <- train.final %>% mutate(Precision.Prediction = ifelse(train.df0 == FALSE, 0, 1))
final.train0 <- d0[,-12]
```

# Logistic Regression on Testing data (optimized for precision and conservative investors)

```{r}
test.final0 <- cbind(data.test, fit.glm.pred.test0)
t0 <- test.final0 %>% mutate(Precision.Prediction = ifelse(fit.glm.pred.test0 == FALSE, 0, 1))
final.test0 <- t0[,-12]
```

```{r}
logit.conservative.data <- rbind(final.train0, final.test0)
```

# Generating the prediction data frame on recall-focused model

```{r}
train.df <- predict(fit_logi5, data.train, type = "response") >= 0.2
train.final <- cbind(data.train, train.df)
d <- train.final %>% mutate(Recall.Prediction = ifelse(train.df == FALSE, 0, 1))
final.train <- d[,-12]

```

# Logistic Regression on Testing data

```{r}
test.final <- cbind(data.test, fit.glm.pred.test)
t <- test.final %>% mutate(Recall.Prediction = ifelse(fit.glm.pred.test == FALSE, 0, 1))
final.test <- t[,-12]
```

```{r}
logit.reg.data <- rbind(final.train, final.test)
```

# Generating the prediction data frame on Random Forest model

```{r}
rf.train <- predict(fit.rf.train, newdata=data.train.rf, type = "response")
train.rf.final <- cbind(data.train.rf, rf.train)
colnames(train.rf.final)[12] <- "Random.Forest.Prediction"

rf.test <- predict(fit.rf.train, newdata=data.test.rf, type = "response")
test.rf.final <- cbind(data.test.rf, rf.test)
colnames(test.rf.final)[12] <- "Random.Forest.Prediction"
```

```{r}
rf.data <- rbind(train.rf.final, test.rf.final)
```

# Merging the data together

```{r}
logit.conservative.merged <- merge(cleaned.data, logit.conservative.data, by = "sentiment")
logit.reg.merged <- merge(cleaned.data, logit.reg.data, by = "sentiment")
rf.merged <- merge(cleaned.data, rf.data, by = "sentiment")
colnames(final.merged)[5] <- "Have at least one star"
```

```{r}
merged.df0 <- left_join(rf.merged, logit.reg.merged, by = "Restaurant")
merged.df1 <- merge(merged.df0, logit.conservative.merged, by = "Restaurant")
final.merged <- merged.df1[,c(1, 76, 51, 26, 75, 55, 73, 54, 67, 74, 69:72, 68, 52)]
colnames(final.merged)[5] <- "Have.min.one.star"
```

```{r}
final.merged %>% group_by(Restaurant, Precision.Prediction, Have.min.one.star, Michelin.Stars) %>% summarise()

precision.final <- final.merged %>% group_by(Restaurant, Precision.Prediction, Have.min.one.star, Michelin.Stars) %>% summarise() %>% filter(Precision.Prediction == 1) %>% distinct(Restaurant)
precision.final <- precision.final[-c(4, 9),]
precision.final

Recall.final <- final.merged %>% group_by(Restaurant, Recall.Prediction, Have.min.one.star, Michelin.Stars) %>% summarise() %>% filter(Recall.Prediction == 1 & Have.min.one.star == 0) %>% distinct(Restaurant)
Recall.final <- Recall.final[-c(5:6, 11:12, 18:19, 44:45),]
Recall.final

Random.Forest.final <- final.merged %>% group_by(Restaurant, Random.Forest.Prediction, Have.min.one.star, Michelin.Stars) %>% summarise() %>% filter(Random.Forest.Prediction == 1 & Have.min.one.star == 0) %>% distinct(Restaurant)
Random.Forest.final <- Random.Forest.final[-c(1:2, 5:6, 11:12, 18),]
Random.Forest.final
```









